A North Sámi to South Sámi machine translation prototype

### 2014-02-10 paper/paper.tex
Reverting to last version , it seems Fran and I have different xetex.

\usepackage{covington}

@@

\begin{abstract}

This paper describes the development of a rule-based
machine translation system from North Sámi to South
Sámi, and its evaluation in a setting where North Sámi
functions as pivot translation via manual translation
from Norwegian North Sámi, and thereafter MT to South Sámi.

\end{abstract}

@@

Previous work

\cite{tyers09} and \cite{wiechetek10} and \cite{trosterud12}

LREC for numbers for the sme-analyser:

\cite{AntonsenEtalReusing2010}

pivot translation references --babych paper

\cite{babych2007}

\section{Motivation}

sma sociolinguistic situation \cite{Todalsvahken2007}

@@

The North Saami analyser has an F-score of 0.93 for morphological disambiguation
and assignment fof grammatical functions \cite{AntonsenEtalReusing2010}.

@@

Here is some facts about the South Saami analyser, if we need it \cite{smadis2011}.

@@

WER -- word error rate
\begin{table}
  \begin{center}
    \begin{tabular}{|l|r|r|r|}
      \hline
      & \textbf{Eval. A} & \textbf{Eval. B} & \textbf{Eval. C}  \\
      \hline
\textbf{WER} (\%) & 62.37  &  49.46  &  52.69 \\
\textbf{PER} (\%) &  36.20   &  28.32  &  28.32 \\
      \hline
    \end{tabular}
    \label{table:coverage2}
    \caption{Evaluation metrics.}
  \end{center}
\end{table}

>>>>

@@

\begin{abstract}
This paper describes the development of a rule-based
machine translation system from North Sámi to South
Sámi, and its evaluation in a setting where North Sámi
functions as pivot translation via manual translation
from Norwegian North Sámi, and thereafter MT to South Sámi. 
\end{abstract}

@@

% Previous work
\cite{tyers09} \cite{wiechetek10} \cite{trosterud12}
% LREC for numbers for the sme-analyser:
\cite{AntonsenEtalReusing2010}

%pivot translation references --babych paper
\cite{babych2007}

\section{Motivation}
sma sociolinguistic situation \citep{Todalsvahken2007}

@@

The North Saami analyser has an F-score of 0.93 for morphological disambiguation
and assignment fof grammatical functions \citep{AntonsenEtalReusing2010}.

@@

Here is some facts about the South Saami analyser, if we need it \citep{smadis2011}.

@@

WER -- word error rate
\begin{table}
  \begin{center}
    \begin{tabular}{|l|r|r|r|}
      \hline
      & \textbf{Eval. A} & \textbf{Eval. B} & \textbf{Eval. C}  \\
      \hline
\textbf{WER} (\%) & 62.37  &  49.46  &  52.69 \\
\textbf{PER} (\%) &  36.20   &  28.32  &  28.32 \\
      \hline
    \end{tabular}
    \label{table:coverage}
    \caption{Evaluation metrics.}
  \end{center}
\end{table}
